---
title: "My First Markdown Document"
author: "The Medium R Team"
date: "The Best Day Ever"
output: html_document
---

# My First Section

We just created our first section in this document. Spacing is very important in markdown, so be sure to leave a blank line after the hashtag heading.

We create a new parapgrah by leaving a blank line.
A new line is considered part of the same paragraph. Only a blank line in between lines of text starts a paragraph.

# Another Section

We start a new section with a single hashtag. No need to close the previous section, just start a new one.

# Let's Talk About Subsections

To create a subsection, within a section, use two hashtags.

## First Subsection

This is a subsection underneath the section that came right before. No need to denote anything, markdown learns from the order.

## Second Subsection

Start another subsection, still within the prior section, with two hashtags. Again, no need to close the previous subsection.

# Back to Sections

Return to sections with a single hashtag to start a new one. No need to close the subsection. Very simple.

# Lists

## Unordered Lists

- Apples
- Bananas
- Oranges
- Kiwis

## Ordered Lists

1. New York
1. New Jersey
1. Naples
1. Detroit
1. Rome

a. Coal
a. Wood
a. Gas

# Formatting

_Text in here is emphasized_

This text will be __strong text__ because of the underscores

Three underscores will make the text ___emphasized and strong___

Backticks creates `typewriter` font

# Links

[Link to my website](https://www.jaredlander.com)

# R Time!!!!!!!!!!!!!!!!!

Now we get to do R! We write R code inside of code chunks, which you can create with the keyboard shortcut `Alt-Ctrl-I`.

```{r addition-example}
1 + 1
```

```{r variables}
x <- 3
x
```

Let's see if we can use the `x` variable in a subsequent chunk.

```{r multiplication}
x * 2
```

```{r try-y, error=TRUE}
y
```

Let's see the result of code but not the code itself.

```{r simple-addition,echo=FALSE}
z <- 10
x + z
```

